### 2018-03-11 paper/3-compute.tex
Minor revision

This section presents purely functional abstractions for build systems that
allow us to express all the intricacies of build systems discussed in the
previous section~\S\ref{sec-background} and design complex build systems from
simple primitives. Specifically, we present the \emph{compute} and \emph{build}
abstractions:

@@

\noindent
\hs{Compute} represents an abstract set of \emph{build tasks}, for example, build
rules in software build systems or formulas in spreadsheets. It is completely
isolated from the world of compilers, file systems, calculation chains, memories,
caches, and all other complexities of real build systems. We explain the compute
type in~\S\ref{sec-general-compute}, and then discuss several noteworthy special
cases: functorial (\S\ref{sec-compute-functor}), applicative
(\S\ref{sec-compute-applicative}) and monadic (\S\ref{sec-compute-monad}) types
of compute.

\hs{Build} corresponds to the algorithm used for bringing a key-value store
\store to a consistent state by recomputing out-of-date values in an
appropriate order. We explain the build type and use it to develop a formal
definition of build systems in~\S\ref{sec-general-build}.
Sections~\S\ref{sec-build} and~\S\ref{sec-implementations} further deconstruct
build algorithms and provide concrete implementations for several build systems.

@@

>>>>

This section presents purely functional abstractions that allow us to express
all the intricacies of build systems discussed in the previous
section~\S\ref{sec-background} and design complex build systems from simple
primitives. Specifically, we present the \emph{compute} and \emph{build}
abstractions:

@@

\noindent
\hs{Compute} represents an abstract set of \emph{build tasks}, for example, build
rules in software build systems or formulas in spreadsheets. It is completely
isolated from the world of compilers, file systems, calculation chains, caches,
and all other complexities of real build systems. We explain the compute type
in~\S\ref{sec-general-compute}, and then discuss several noteworthy special
cases: functorial (\S\ref{sec-compute-functor}), applicative
(\S\ref{sec-compute-applicative}) and monadic (\S\ref{sec-compute-monad}) types
of compute.

\hs{Build} corresponds to the algorithm used for bringing a key-value store
\store to a consistent state by recomputing out-of-date values in an
appropriate order. We explain the build type and use it to develop a formal
definition of build systems in~\S\ref{sec-general-build}.
Sections~\S\ref{sec-build} and~\S\ref{sec-implementations} scrutinise the build
abstraction further and provide concrete implementations for several build
systems.

@@

\subsection{Free build structures}\label{sec-free-build}

\begin{minted}{haskell}
data Depend k v r = Depend [k] ([v] -> r)

data Depends k v r = Depends [k] ([v] -> Depends k v r)
                   | Done r
\end{minted}
